---
title: "Assignment 2 Report"
author: "Taylor Falk"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Please read this brief introduction to R Markdown, and complete the second half of the document yourself.**

# R Markdown
R Markdown, `.Rmd` files, are a type of markdown files that can execute R code in an R environment. Markdown is an open source language used for easily creating documents such as web pages and PDFs. Markdown and R Markdown can be used to procedurally generate documents and reports, which have a wide number of use-cases across bioinformatics. Not only can you save time by creating code to automatically draft documents, you can also include detailed instructions and information alongside your code.

## knitr
`knitr` is simply the package R uses to convert the R Markdown into the appropriate output (HTML, PDF, or Word). While there is a deep level of customization available, most users can comfortably create beautiful documents with the default parameters. In order to compile your markdown, in RStudio you can select the `Knit` button below the open file button.

---

## Markdown Basics
The raw markdown, which you may or may not be looking at, is styled very basically. The largest titles start with one octothorpe `#`. The more `#`'s added, the smaller a title or header becomes.  

# Biggest  
## 2nd Biggest  
### so on  
#### and so forth  
##### until you have  
###### six octothorpes  
####### then nothing happens.

Importantly, two spaces (`  `) can be included after a line of text to start a new line.

Markdown can be styled a few different ways:  
`_italics_` -> _italics_  
`**bold**` -> **bold**  
`` `monospace` `` -> `monospace`, good for code  

A good cheat sheet is the [Markdown Guide Cheat Sheet](https://www.markdownguide.org/cheat-sheet)

---

## R Code in Markdown
The really vital part of R Markdown is the inclusion of code snippets you can place into the document, which will run and print out to users. In this snippet I create a function that says hello and that text is printed inside the document.
```{r}
say_hi <- function() {
  return("Hello world.")
}
print(say_hi())
```

The syntax of the **snippet* is simple, with three back ticks ` ``` ` indicating the start and end of the snippet, and a lower case `r` in curly braces `{}` to indicate what language is used: `{r}` indicates R, `{python}` indicates Python. R Markdown does not support every language, but there are use cases where one document running both R and Python code can prove extremely useful and concise. There is also a button in RStudio to insert a snippet, it is a small green `+C` in the top right of the editor.

```{python}
import datetime
print(f'Wishing you a wonderful hello from Python at {datetime.datetime.now()}')
```
I can also test my code in RStudio without having to knit the entire document by pressing the green "Play" arrow on the snippet I am interested in.

Finally, R Markdown scripts can `source()` other `.R` scripts and use them in their execution environment. This mean I can define a function in my `main.R` script and use it in my R Markdown snippets. Note that the converse is true, using `knitr::purl()`, and the code established in an R Markdown can be sourced, and _tested_, using an normal `.R` script.

Also note that the environment is carried from one snippet to another, so if I define a function or load a file in one snippet I can use those objects in later snippets. 

```{r}
message <- 'The last example...for now.'
```
```{r}
print(paste(message, 'But there\'s always room for more.'))
```


# Assignment
Using what you now know from both plotting and data manipulation, use ggplot to create 

